fdcoexist

### 2018-08-21 paper_simulations.Rmd
:sparkles: :art: add all traits CWMs in synthetic plot

@@

# Compute linear models for CWM <-> environment relationship
mod_df <- all_df %>%
    group_by(env_width, compet_status, cor_level, scenario, patch) %>%
    summarise(patch_optim = unique(patch_optim), trait2_cwm = sum(trait2_cwm)) %>%
    nest() %>%
    mutate(mod_cwm_env = map(data, ~lm(trait2_cwm ~ patch_optim, data = .x)),
           mod_glance = map(mod_cwm_env, broom::glance)) %>%
    unnest(mod_glance)

# R2 plot
plot_r2_cwm_env = ggplot(mod_df, aes(scenario, r.squared)) +
    geom_point(aes(fill = fct_rev(cor_level)),
               size = 4, position = position_dodge(width = 0.7),
               shape = 21) +
    facet_grid(rows = vars(compet_status), cols = vars(env_width),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "No Competition"),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                               varying  = "Varying\nEnv. Filter Strength"))) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    guides(color = FALSE,
           fill = guide_legend(override.aes = list(shape = 21,
                                                   size = 4))) +
    labs(subtitle = "R2 of trait2 CWM ~ environment",
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

>>>>

## Without Compettiion

@@

# Compute linear models for CWM <-> environment relationship
mod_df <- all_df %>%
    gather("cwm_name", "cwm_value", contains("cwm")) %>%
    group_by(env_width, compet_status, cor_level, scenario, patch, cwm_name) %>%
    summarise(patch_optim = unique(patch_optim), cwm_value = sum(cwm_value)) %>%
    group_by(env_width, compet_status, cor_level, scenario, cwm_name) %>%
    nest() %>%
    mutate(mod_cwm_env = map(data, ~lm(cwm_value ~ patch_optim, data = .x)),
           mod_glance = map(mod_cwm_env, broom::glance)) %>%
    unnest(mod_glance)

# R2 plot
plot_r2_cwm_env = ggplot(mod_df, aes(scenario, r.squared)) +
    geom_point(aes(fill = fct_rev(cor_level)),
               size = 4, position = position_dodge(width = 0.7),
               shape = 21) +
    facet_grid(rows = vars(compet_status), cols = vars(env_width, cwm_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "No Competition"),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength"))) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    guides(color = FALSE,
           fill = guide_legend(override.aes = list(shape = 21,
                                                   size = 4))) +
    labs(subtitle = "R2 of trait2 CWM ~ environment",
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")
